---
title: "Homework1"
format: html
editor: visual
---

## Data Science Questions

**What do you think being a data scientist is about?**

-   Data scientists will use computer programming/software and basic to advanced statistical methods to gather, import, interpret, and visualize data. Data scientists often will create statistical models to make predictions.

**What differences/similarities do you see between data scientists and statisticians?**

-   Statisticians are more likely to approach questions with respect to testing specific hypotheses, research methodology, and tightly controlled study designs. Most statisticians work in academic or research settings.

-   Data Scientists are more likely to use exploratory analysis and data mining techniques on larger and messier sets of data. There is less of a focus on methodological rigor in their analyses. Data scientists often focus on prediction and classification. Most data scientists work in industry settings.

-   Both roles rely on the same math and statistical foundations and are concerned with the accuracy and validity of their analyses.

**How do you view yourself in relation to these two areas?**

-   I am a professional focusing on business intelligence and am interested in a more rigorous study of statistical theory and methods while learning technical skills necessary to effectively transition to data science work.

## Iris Dataset

Storing density() function results in object y.

```{r}
y <- density(iris$Petal.Width)
```

Finding the class of object y.

```{r}
class(y)
```

Finding the type of object y.

```{r}
typeof(y)
```

Finding the structure of object y.

```{r}
str(y)
```

Here is a plot of the object y (with the code hidden)!

```{r}
#| echo: false
plot(y)
```
